Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-08-22 manuscript.tex
overleaf update
Update on Overleaf.

\begin{abstract*} 
Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we put a differential readout SNSPD to the ultimate test. We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50\textasciitilde ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.
\end{abstract*}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{fig:channel_data}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=\textheight]{chapter_03/figs_03/8ch_bar_graph_high_power_light.pdf}
\caption[{Fidelity and rates across 8 channel pairs.}]{\textbf{Fidelity and rates across 8 channel pairs} a) Fidelity for the main 8 channel pairs, measured at a high (5.17 Amps) and a low ( 1.2 Amps) SHG pump power setting. Each power setting results in similar \(\mu\) for all channels: \(\mu_{low}\) = 5.6e-5 \(\pm\) 9e-6 and \(\mu_{high}\) = 6.1e-3 \(\pm\) 3e-4. b) Rate metrics for the 8 channel pairs at the same high and low power settings. The range of possible values for distillable entanglement rate is spanned by the yellow regions, bounded above by log-negativity and below by coherent information. Rates shown assume readout of all 4 available interferometer ports, based on data measured using one port each at Alice and Bob}
\label{fig:channel_data}
\end{figure}
}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

>>>>

\begin{abstract*}

\end{abstract*}

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Abstract}

Photon number resolution is an emerging capability of advanced Superconducting Nanowire Single Photon Detectors. If leveraged to it's full potential, PNR capabilty can have a profound impact on the usefulness of SNSPDs is certain quantum applications including linear optical quantum computing, quantum networks, and quantum sensing. Discrimination of not just the number of photons in an optical pulse but also pulse arrival time with high accuracy is an open problem, complicated by the nuanced way in which these two degrees of freedom are intertwined in the response function of these detectors. In this work we put a differential readout SNSPD to the ultimate test. We test it's capabilities in a Pulse Position Modulation experiment whereby data is sent in the arrival time of optical pulses derived from a 20 GHz optical clock. We show the detector is capable of discriminating the arrival time of photons to 50\textasciitilde ps wide bins with high accuracy while simultaneously providing photon number information about the impinging optical pulses. We find that a careful statistical analysis of the PNR response is necessary to back-out a precise measurement of pulse arrival time.

\subsection{Introduction}

@@

\hypertarget{fig:channel_data}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth]{./figs_03/8ch_bar_graph_high_power_light.pdf}
\caption[{Fidelity and rates across 8 channel pairs.}]{\textbf{Fidelity and rates across 8 channel pairs} a) Fidelity for the main 8 channel pairs, measured at a high (5.17 Amps) and a low ( 1.2 Amps) SHG pump power setting. Each power setting results in similar \(\mu\) for all channels: \(\mu_{low}\) = 5.6e-5 \(\pm\) 9e-6 and \(\mu_{high}\) = 6.1e-3 \(\pm\) 3e-4. b) Rate metrics for the 8 channel pairs at the same high and low power settings. The range of possible values for distillable entanglement rate is spanned by the yellow regions, bounded above by log-negativity and below by coherent information. Rates shown assume readout of all 4 available interferometer ports, based on data measured using one port each at Alice and Bob}
\label{fig:channel_data}
\end{figure}
}

this is where I add a citation

\subsection{Methods}
